|

### 2021-12-16 01-Chp-Background.Rmd
Range of updates

(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.

@@

### Mendelian randomisation

Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk. Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:

1. the IV is associated with the exposure of interest (the relevance assumption);
2. the IV and outcome do not share a common cause (the independence assumption); and
3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).

>>>>

(ref:statin-mechanisam-cap) __Statin mechanism of action__ - Statins inhibit HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate. This conversion is the rate-limiting step in cholesterol biosynthesis, and so statin use can lower cholesterol levels.

@@

### Mendelian randomisation {}

Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk. Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV)[@davies2018] which are discussed in Section \@ref(rev-discussion-MR).

### 2021-12-16 03-Chp-Systematic-Review-Methods.Rmd
Range of updates

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic. The formulae used to calculate AC1 are given in Appendix \@ref(appendix-gwet).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated an issue with the screening process (defined as an AC1 of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.

@@

An initial qualitative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design. Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis". <!-- TODO CITATION NEEDED -->

Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading). Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).

>>>>

Rater reliability was assessed using Gwet's agreement coefficient ($AC1$).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does. [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic. The formulae used to calculate $AC$ are given in Appendix \@ref(appendix-gwet).

@@

Intra- and inter-rater reliability was assessed against these cut-offs. If this assessment demonstrated an issue with the screening process (defined as an $AC$ of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.

@@

An initial qualitative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design. Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis". Results were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies). The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(tri-heading). Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).
